Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-07-07 ltx/data_paper/DataPaper.tex
edits to EM for data paper

>>>>

\parham{In the next step the above equation is rearranged in order to isolate the covariance and the cross-covariance terms, enabling the use of smoother outputs. Taking trace and rearranging, applying the invariant cyclic permutations property of the trace, equations \eqref{eq:CondititionDist1} and \eqref{eq:CondititionDist2} become}
